\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}}
% New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document
\usepackage[T1]{fontenc}
\usepackage{tgadventor}
\usepackage[outline]{contour}

\renewcommand{\cvheadingfont}{\LARGE\color{Purple}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Blue, linkcolor=Blue} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.2em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} 
% Define a command for descriptions of each entry - change spacing and font sizes here

%----------------------------------------------------------------------------------------
\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{{\spacedallcaps{Sami Davies}}}\vspace{1.5em} % Your name

% \noindent contact % Personal information heading

\NewEntry{email}{\textsf{\href{sami@northwestern.edu}{sami@northwestern.edu}}} % Email address

\NewEntry{website}{\textsf{\href{samidavies.com}{samidavies.com}}} % Personal website

\NewEntry{position}{\textsf{\href{samidavies.com}{Post-doc at Northwestern CS}}}

\vspace{1em} % Extra white space between the personal information section and goal


\noindent{\color{Purple}Research Objective}\vspace{1em} % Goal heading, could be used for a quotation or short profile instead

\Description{To design algorithms for combinatorial optimization problems that go\\ beyond worst-case analysis
in order to (1) develop a more complete theoretical understanding of a problem's difficulty and (2) provide performance guarantees that are representative of what happens in practice.}
\vspace{-.5cm}
{\color{Purple}\noindent\rule{12cm}{0.4pt}}
\vspace{.1cm}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent {\color{Purple}Education}\vspace{1em}

\MarginText{\scriptsize{University of Washington}}\NewEntry{2016--2021}{\normalsize{Ph.D. in Mathematics}}

\vspace{.5cm}

%------------------------------------------------

\MarginText{ \scriptsize{University of Illinois at Chicago}}\NewEntry{2015--2016}{\normalsize{M.S. in Mathematics}}

\vspace{.5cm}
%------------------------------------------------



\MarginText{ \scriptsize{Carnegie Mellon University}}\NewEntry{2011--2015}{\normalsize{B.S. in Mathematics}}\\
\hspace{3.45cm}\footnotesize{Minor in Economics, College and University Honors}

{\color{Purple}\noindent\rule{12cm}{0.4pt}}
\vspace{.1cm}
% Extra space between major sections

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

%------------------------------------------------



\noindent {\color{Purple}\normalsize{Publications}}\vspace{1em}

\NewEntry{\hspace{-.70cm}{\color{Purple}[1]} \hspace{.5cm}Feb. 2023}{\hspace{.25cm}\small{Fast Combinatorial Algorithms for Min Max}\\
\hspace{3.4cm}\small{Correlation Clustering}}

\Description{\MarginText{ICML 2023}Sami Davies, Benjamin Moseley, Heather Newman}

\vspace{.3cm}



\NewEntry{\hspace{-.90cm}{\color{Purple}[2]} \hspace{.5cm}Oct. 2022}{\hspace{.25cm}\normalsize{Predictive Flows for Faster Ford-Fulkerson}}

\Description{\MarginText{ICML 2023}Sami Davies, Benjamin Moseley, Sergei Vassilvitskii, Yuyan Wang}

\vspace{.3cm}


\NewEntry{\hspace{-1cm}{\color{Purple}[3]} \hspace{.47cm}July 2022}{\small{Robust Factorizations and Colorings of Tensor Graphs}}

\Description{\MarginText{In submission}Joshua Brakensiek, Sami Davies}

\vspace{.3cm}

\NewEntry{\hspace{-1cm}{\color{Purple}[4]} \hspace{.47cm}Feb. 2022}{\normalsize{Balancing Flow Time and Energy Consumption}}

\Description{\MarginText{SPAA 2022}Sami Davies, Samir Khuller, Shirley Zhang}

\vspace{.3cm}

\NewEntry{\hspace{-1cm}{\color{Purple}[5]} \hspace{.47cm}Sept. 2021}{\small{New Lower Bounds on the Total Variation Distance}\\  \hspace{3.35cm} \small{Between Mixtures of Two Gaussians}}

\Description{\MarginText{ALT 2022}Sami Davies, Arya Mazumdar, Soumyabrata Pal, Cyrus Rashtchian}

\vspace{.3cm}

\NewEntry{\hspace{-1cm}{\color{Purple}[6]} \hspace{.47cm}July 2021}{\small{On the Hardness of Scheduling with Non-} \\
\hspace{3.5cm}\small{Uniform Communication Delays}}

\Description{\MarginText{SODA 2022}Sami Davies, Janardhan Kulkarni, Thomas Rothvoss, Sai Sandeep, Jakub Tarnawski, Yihao Zhang}

\vspace{.3cm}

\NewEntry{\hspace{-1cm}{\color{Purple}[7]} \hspace{.47cm}July 2021}{\normalsize{Approximate Trace Reconstruction: Algorithms}}

\Description{\MarginText{ISIT 2021}Sami Davies, Mikl\'os Z.\ R\'acz, Benjamin Schiffer, Cyrus Rashtchian}

% \vspace{.3cm}
\clearpage

\NewEntry{\hspace{-1cm}{\color{Purple}[8]} \hspace{.47cm}July 2020}{\small{Scheduling with Communication Delays}\\
\hspace{3.45cm}\small{via LP Hierarchies and Clustering II: Weighted}\\
\hspace{3.43cm}\small{Completion Times on Related Machines}}

\Description{\MarginText{SODA 2021}Sami Davies, Janardhan Kulkarni, Thomas Rothvoss, Jakub Tarnawski, Yihao Zhang}

\vspace{.3cm}

\NewEntry{\hspace{-1cm}{\color{Purple}[9]} \hspace{.47cm}April 2020}{\small{Scheduling with Communication Delays via LP\\
\hspace{2.7cm}Hierarchies and Clustering}}

\Description{\MarginText{FOCS 2020}Sami Davies, Janardhan Kulkarni, Thomas Rothvoss, Jakub Tarnawski, Yihao Zhang}

\vspace{.3cm}

\NewEntry{\hspace{-1cm}{\color{Purple}[10]} \hspace{.47cm}July 2018}{\small{A Tale of Santa Claus, Hypergraphs and Matroids}}

\Description{\MarginText{SODA 2020}Sami Davies, Thomas Rothvoss, Yihao Zhang}

\vspace{.3cm}

\NewEntry{\hspace{-1cm}{\color{Purple}[11]} \hspace{.3cm}Jan. 2019}{\normalsize{Reconstructing Trees from Traces}}

\Description{\MarginText{COLT 2019}Sami Davies,	Mikl\'os Z.\ R\'acz, Cyrus Rashtchian. Full version in the Annals of Applied Probability 31(6): 2772--2810, 2021}

{\color{Purple}\noindent\rule{12cm}{0.4pt}}
%------------------------------------------------

% \NewEntry{Sept. 2012}{Predictive Flows for Faster Ford-Fulkerson}

% \Description{\MarginText{Full Journal Name}Lorem ipsum dolor sit amet, consectetur adipiscing elit. Ut nisl tellus, sodales non pulvinar in, adipiscing sit amet purus. Suspendisse sed facilisis diam. Sed ornare sem nec justo adipiscing nec venenatis lectus commodo. Mauris non neque ligula. Pellentesque sed quam eu felis iaculis iaculis ac a leo. Suspendisse neque neque, placerat id adipiscing et, elementum eu sem.\\ Authors: John \textsc{Smith}, ~James \textsc{Smith}}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

% \header{Recent invited participation and internships}

\noindent {\color{Purple}\large{Recent Invited Participation and Internships}}\vspace{1em}

\Description{\MarginText{Sept. 2023}\normalsize{Simons Institute}\\
\footnotesize{Program on Logic and Algorithms in Database Theory and AI}}


\Description{\MarginText{Sept. 2023}\normalsize{Banff International Research Station (BIRS)}\\
\footnotesize{Approximation Algorithms and the Hardness of Approximations workshop}}

\Description{\MarginText{Feb. 2023}\normalsize{Dagstuhl Seminar in Scheduling}\\
\footnotesize{1 of 5 invited hour long talks}}

\Description{\MarginText{Oct. 2022}\normalsize{EECS Rising Stars}\\
\footnotesize{Workshop, held at UT Austin in 2022}}

\Description{\MarginText{June 2022}\normalsize{TCS Women Rising Stars at STOC 2022}\\ 
\footnotesize{Virtual talk on robust tensor factorization}}

\Description{\MarginText{May 2022}\normalsize{IDEAL Workshop on Algorithms for Massive Data Sets}\\
\footnotesize{Virtual talk on learning-augmented algorithms}}

\Description{\MarginText{May 2021}\normalsize{CanaDAM(Canadian Discrete and Algorithmic Mathematics)}\\ 
\footnotesize{Virtual talk on scheduling with communication delays}}

\Description{\MarginText{Summer 2020}\normalsize{Microsoft Research, Redmond Intern}\\
\footnotesize{Hosted by Janardhan Kulkarni and Jakub Tarnawski in the Algorithms group}}

\Description{\MarginText{Feb. 2020}\normalsize{Dagstuhl Seminar in Scheduling}\\
\footnotesize{Talk on the Santa Claus problem}}


{\color{Purple}\noindent\rule{12cm}{0.4pt}}

\vspace{1em}
\noindent {\color{Purple}Awards and Fellowships}\vspace{1em}

\Description{\MarginText{2021-2023}\normalsize{NSF Computing Innovation Fellow}\\
\footnotesize{Awarded funding for a two-year post-doctoral fellowship}}

\Description{\MarginText{2020}\normalsize{Tanzi-Egerton Fellow}\\
\footnotesize{Awarded to an outstanding senior graduate student in mathematics at UW}}

\Description{\MarginText{2020}\normalsize{Microsoft Research Dissertation Grant}\\
\footnotesize{Awarded to ten graduate students in computer science across the US}}

\Description{\MarginText{2017-2019}\normalsize{McKibben and Merner Endowed Fellowship in Mathematics}\\
\footnotesize{Awarded to two mathematics Ph.D. students at UW who were exceptional in their preliminary exams and first-year courses}}

{\color{Purple}\noindent\rule{12cm}{0.4pt}}

\vspace{1em} 

\noindent {\color{Purple}Teaching}\vspace{1em}


I taught the following courses:
\begin{center}
	\begin{tabular}{ l l l }
	  \textbf{Math 107}& Math in Society & \footnotesize{FEPPS Summer 2018} \\ 
	  \textbf{CSE 311}&	 Foundations of Computing I & \footnotesize{UW Spring 2020}	
	\end{tabular}
\end{center}

I served as a teaching assistant for the following courses:
\begin{center}
	\begin{tabular}{ l l l }
	  \textbf{Math 111}& Algebra with Applications & \footnotesize{UW Fall 2017} \\ 
	  \textbf{Math 124}&	 Calculus I & \footnotesize{UW Winter  \& Spring 2017}  \\  
	 \textbf{Math 126} &    Multivariable Calculus   & \footnotesize{UW Fall 2016}    \\
	\textbf{Math 121}	& Pre-Calculus	& \footnotesize{UIC Fall 2015 \& Spring 2016}\\	
	\textbf{21-241}	&	Matrices \& Linear Transformations & \footnotesize{CMU Spring 2015 }
	\end{tabular}
\end{center}

{\color{Purple}\noindent\rule{12cm}{0.4pt}}

\vspace{1em}

\noindent {\color{Purple}Service and Outreach}\vspace{1em}

\Description{\large{External Reviewer}\\
\footnotesize{SODA 2020, ICALP 2020, \emph{IEEE Transactions on Information Theory}, MFCS 2020, ISAAC 2020, \emph{Operations Research}, 
PODS 2021, WADS 2021, ICALP 2021, STOC 2022, ICALP 2022, ESA 2022, \emph{Discrete Mathematics}, ISAAC 2022, SODA 2023, \emph{Algorithmica}, 
FOCS 2023}}

\Description{\large{PC Member}\\
\footnotesize{APPROX 2023, WAOA 2023, IPCO 2024}}

\Description{\MarginText{Dec. 2021}\large{Co-organizer 2021 Northwestern Junior Theorists Workshop}\\
\footnotesize{Co-organized a workshop highlighting rising theoretical computer scientists. https://theory.cs.northwestern.edu/events/2021-junior-theorists-workshop/}}

\Description{\MarginText{2018-2021}\large{Washington Directed Reading Program}\\
\footnotesize{Mentored for the WDRP, a program that pairs undergraduate students with graduate students for independent reading projects. Helped conceive and write grants for the WDRP in summer 2018.}}

\Description{\MarginText{2021}\large{Mastery Learning Hour}\\
\footnotesize{Tutored math for K-12 students. Provided support to students during COVID-19 pandemic.}}

\Description{\MarginText{2017-2019}\large{Freedom Education Project Puget Sound (FEPPS)}\\
\footnotesize{Tutored incarcerated women during the fall and winter of 2017. Served as the course co-instructor for Math 107 during the summer of 2018 at the Washington Corrections Center for Women.}}

\Description{\MarginText{2018}\large{Math Circle}\\
\footnotesize{Served as an instructor during the spring of 2018.}}

% \Description{\MarginText{2016-2021}\large{Assocation for Women in Math}\\
% \footnotesize{Served as secretary of the UW student chapter during the 2018-2019 academic year.}}


\end{cv}

\end{document}